The brightness and spatial distributions of terrestrial radio sources

### 2013-07-22 articles/Article-RFI-distribution/article-rfi-distribution.tex
Inserting correct dates
Submitted article to Arxiv

$^{33}$Argelander-Institut f\"{u}r Astronomie, University of Bonn, Auf dem H\"{u}gel 71, 53121, Bonn, Germany

@@

\date{Accepted [TODO date]. Received [TODO date]; in original form [TODO date]}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\pubyear{2013}

>>>>

$^{33}$Argelander-Institut f\"{u}r Astronomie, University of Bonn, Auf dem H\"{u}gel 71, 53121, Bonn, Germany\vspace*{-0.5cm}

@@

\date{Accepted 2013 July 16. Received 2013 July 16; in original form 2013 March 1}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\pubyear{2013}
